---
title: "Senior Thesis"
subtitle: "subtitle"
author: "Jonathan D. Trattner"
date: "date"
output:
  xaringan::moon_reader:
    lib_dir: libs
    seal: false
    nature:
      beforeInit: "my-macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    css: jdtrat.css
---
class: inverse center middle

# Senio*R* Thesis

.large[Jonathan Trattner | 05-07-2021]

```{r setup-main, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanExtra)
xaringanExtra::use_xaringan_extra(include = c("tile_view", "editable", "animate_css", "tachyons", "share_again", "fit_screen", "search", "scribble", "webcam"))
```


```{r meta, echo=FALSE}
library(metathis)
metathis::include_meta(
  meta() %>%
  meta_general(
    description = "",
    generator = "xaringan and remark.js"
  ) %>% 
  meta_social(
    title = "SenioR Thesis",
    url = "",
    image = "",
    image_alt = "",
    og_type = "website",
    og_author = "Jonathan David Trattner",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@jdtrat"
  )
)
```

---
class: inverse center middle

# Hello, World.

???

---
name: theme
layout: true
.my-header[
]

.my-footer[
]

---
class: top
.my-header[
.title[
What is R?
]
]

--

.absolute.left-2.top--1.mt4[
![:r_logo]
]

???
R is a letter. Between Q and S.

--

.relative.top-2.mt5.left-2.ml5.f2.tl.lh-title.pt7[
.relative.top-0.pt3[
is a letter between Q and S.
]
]

???
In computer land, R is what's known as an interpreted, object oriented language. 
A descendent of S, a statistical analysis environment developed at Bell Laboratories -- part of AT&T -- in the 1970s.


---
class: top
.my-header[
.title[
What is R?
]
]

.absolute.left-2.top--1.mt4[
![:r_logo]
]

.relative.top-2.mt5.left-2.ml5.f2.tl.lh-title.pt7[
.relative.top-0.pt3[
is .strike[a letter between Q and S.]
]
]

.relative.left-2.ml5.f2.tl.lh-title[
.relative.left-2.r-color.top-0[an interpreted, .underline[object-oriented] language.]
]

???
In computer land, R is what's known as an interpreted, object oriented language. 
A descendent of S, a statistical analysis environment developed at Bell Laboratories -- part of AT&T -- in the 1970s.

---
class: top center
.my-header[
.title[Why R?
]
]

.mt6.top-2.pt2.f2.lh-title.black.ml0[

.gradient-list.can-edit[
* It's free `r emo::ji("money_mouth_face")`
* It is easily extendible with `r emo::ji("package")`
* It has a vibrant community of use.r-color.b[R]s
]
]

???

First and foremost, R is free unlike some other statistical softwares used in academia like SPSS or Stata. Secondly, it's easily extendible and open source. So, as we will see, anyone can develop a package with code that is easily usable by others. Thirdly, it has a vibrant community of users and developers all of whom are super nice. There's a lot of discussion with people of all skill-levels about how to make R the best for the most people.

Another benefit, not on the slide because I'm going to get into it more, is R's easy integration with other programming languages. So, R itself is derived from the language S, but its creators Ross Ihaka and Robert Gentleman took lots of inspiration from Scheme. A lot of R is actually written in C and C++ to optimize performance, and there a many packages that help users integrate these languages. 

What I'm going to focus on today is R's integration with HTML, CSS, and JavaScript.

---
class: top center
.my-header[
.title[
Talk R 2 Me
]
]


.f2.lh-copy.mt6.tc.bb.bt.br3.bw2.b--green[
Websites are mainly built with three languages.
]

.relative.flex.justify-between.top--2.mt5.tc[

.mr2.column.w-33.ph3.bg-washed-green.dark-gray.b--green.ba.bw1.br3.ph3.pv0.shadow-5[

.center.b[HTML]

.f4[Defines the structure of websites.]
]

.mr2.column.w-33.ph3.bg-washed-green.dark-gray.b--green.ba.bw1.br3.ph3.pv0.shadow-5[
.center.b[CSS]

.f4[Defines the aesthetics of websites.]
]

.mr2.column.w-33.ph3.bg-washed-green.dark-gray.b--green.ba.bw1.br3.ph3.pv0.shadow-5[
.center.b[JavaScript]

.f4[Defines the behavior of websites.]

]
]

---
class: top center
.my-header[
.title[
Talk R 2 Me
]
]


.f2.lh-copy.mt6.tc.bb.bt.br3.bw2.b--green[
Websites are .strike[mainly] .r-color[also] built with .strike[three languages] .r-color[R].
]

.w-25.relative.pt2.top-1[
![:shiny]
]

.absolute.mt7.left-2.top-2.ml7.pt6.w-60.tl[
Shiny allows users to combine R's computational power with the interactivity of web applications.
]

